### 2023-12-28 sections/4-results.tex
merged table for results

Tables \ref{tab:results:fashion-mnist}, \ref{tab:results:glove-25}, \ref{tab:results:sift}, and \ref{tab:results:random} show the throughput and recall of CAKES's algorithms at each augmented cardinality for Fashion-Mnist, Glove-25, Sift, and Random respectively.
Though the scaling plots above present results for each of CAKES's three algorithms separately, the results in the CAKES column in these tables represent the fastest CAKES algorithm at that dataset and cardinality only.
We used our auto-tuning approach (see Section~\ref{sec:methods:auto-tuning}) for each new tree (i.e. at each cardinality), and this approach was always able to select the fastest algorithm for each dataset at each cardinality.
Since we also allow for tuning hyper-parameters for the other algorithms, and we allow for different sets of hyper-parameters at each cardinality, it is a fair comparison for these tables to only list the performance of the tuned CAKES algorithm.
When reporting recall, we use $1.000*$ to denote that the recall is imperfect, but rounds to $1.000$ when we consider only three decimal places.

@@

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{fashion-mnist} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:fashion-mnist}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Multiplier}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                        & QPS                 & Recall & QPS                & Recall & QPS                & Recall& QPS                 & Recall \\
                    \hline
                    1   & 1.33~$\times10^{4}$ & 0.954 & 2.19~$\times10^{3}$ & 0.950 & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000 \\
                    \hline
                    2   & 1.38~$\times10^{4}$ & 0.803 & 2.12~$\times10^{3}$ & 0.927 & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000 \\
                    \hline
                    4   & 1.66~$\times10^{4}$ & 0.681 & 2.04~$\times10^{3}$ & 0.898 & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 1.68~$\times10^{4}$ & 0.525 & 1.93~$\times10^{3}$ & 0.857 & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000 \\
                    \hline
                    16  & 1.87~$\times10^{4}$ & 0.494 & 1.84~$\times10^{3}$ & 0.862 & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000 \\
                    \hline
                    32  & 1.56~$\times10^{4}$ & 0.542 & 1.85~$\times10^{3}$ & 0.775 & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000 \\
                    \hline
                    64  & 1.50~$\times10^{4}$ & 0.378 & 1.78~$\times10^{3}$ & 0.677 & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000 \\
                    \hline
                    128 & 1.49~$\times10^{4}$ & 0.357 & 1.66~$\times10^{3}$ & 0.538 & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & 1.60~$\times10^{3}$ & 0.592 & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000 \\
                    \hline
                    512 & --                  & --    & 1.83~$\times10^{3}$ & 0.581 & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{glove-25} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:glove-25}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Multiplier}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000* \\
                    \hline
                    2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000* \\
                    \hline
                    4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000* \\
                    \hline
                    8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000* \\
                    \hline
                    16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000* \\
                    \hline
                    32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000* \\
                    \hline
                    64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000* \\
                    \hline
                    128 & --                  & --    & --                  & --    & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000* \\
                    \hline
                    256 & --                  & --    & --                  & --    & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000* \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{sift} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:sift}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Multiplier}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\
                    \hline
                    16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\
                    \hline
                    32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on a \textbf{random} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:random}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Multiplier}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1  & 1.17~$\times10^{4}$ & 0.060 & 4.28~$\times10^{3}$ & 0.028 & 7.34~$\times10^{2}$ & 1.000* & 5.54~$\times10^{2}$ & 1.000 \\
                    \hline
                    2  & 1.01~$\times10^{4}$ & 0.048 & 4.04~$\times10^{3}$ & 0.021 & 3.58~$\times10^{2}$ & 1.000* & 2.69~$\times10^{2}$ & 1.000 \\
                    \hline
                    4  & 9.12~$\times10^{3}$ & 0.031 & 3.64~$\times10^{3}$ & 0.014 & 1.90~$\times10^{2}$ & 1.000* & 1.37~$\times10^{2}$ & 1.000 \\
                    \hline
                    8  & 8.35~$\times10^{3}$ & 0.022 & 3.37~$\times10^{3}$ & 0.013 & 8.84~$\times10^{1}$ & 1.000* & 5.69~$\times10^{1}$ & 1.000 \\
                    \hline
                    16 & 8.25~$\times10^{3}$ & 0.008 & 3.17~$\times10^{3}$ & 0.006 & 4.36~$\times10^{1}$ & 1.000* & 2.61~$\times10^{1}$ & 1.000 \\
                    \hline
                    32 & --                  & --    & 3.01~$\times10^{3}$ & 0.007 & 1.72~$\times10^{1}$ & 1.000* & 1.35~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

>>>>

Table~\ref{tab:results:qps-and-recall} show the throughput and recall of CAKES's algorithms at each augmented cardinality for Fashion-Mnist, Glove-25, Sift, and Random.
Though the scaling plots above present results for each of CAKES's three algorithms separately, the results in the CAKES column in these tables represent the fastest CAKES algorithm at that dataset and cardinality only.
We used our auto-tuning approach (see Section~\ref{sec:methods:auto-tuning}) for each new tree (i.e. at each cardinality), and this approach was always able to select the fastest algorithm for each dataset at each cardinality.
Since we also allow for tuning hyper-parameters for the other algorithms, and we allow for different sets of hyper-parameters at each cardinality, it is a fair comparison for these tables to only list the performance of the tuned CAKES algorithm.
When reporting recall, we use $1.000*$ to denote that the recall is imperfect, but rounds to $1.000$ when we consider only three decimal places.

{\color{red} TODO: Combine the following four paragraphs into a single, larger paragraph that summarizes the results across all datasets. There is too much repetition here.}

@@

\begin{table*}[h]
    % \renewcommand{\arraystretch}{1.15}
    \caption{QPS (queries per second) and Recall vs naive linear search on the Fashion-Mnist, Glove-25, Sift and Random datasets.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|c|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    & \multirow{2}{*}{\textbf{Multiplier}} & \multicolumn{2}{|c}{\textbf{hnsw}} & \multicolumn{2}{|c}{\textbf{annoy}} & \multicolumn{2}{|c}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{cakes}} \\\cline{3-10}
                    & & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\\cline{2-10}
                    \hline
                    \hline
                    \multirow{10}{*}{\rotatebox[origin=c]{90}{\textbf{Fashion-Mnist}}}
                    & 1   & 1.33~$\times10^{4}$ & 0.954  & 2.19~$\times10^{3}$ & 0.950  & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 2   & 1.38~$\times10^{4}$ & 0.803  & 2.12~$\times10^{3}$ & 0.927  & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 4   & 1.66~$\times10^{4}$ & 0.681  & 2.04~$\times10^{3}$ & 0.898  & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000  \\\cline{2-10}
                    & 8   & 1.68~$\times10^{4}$ & 0.525  & 1.93~$\times10^{3}$ & 0.857  & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 16  & 1.87~$\times10^{4}$ & 0.494  & 1.84~$\times10^{3}$ & 0.862  & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 32  & 1.56~$\times10^{4}$ & 0.542  & 1.85~$\times10^{3}$ & 0.775  & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 64  & 1.50~$\times10^{4}$ & 0.378  & 1.78~$\times10^{3}$ & 0.677  & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 128 & 1.49~$\times10^{4}$ & 0.357  & 1.66~$\times10^{3}$ & 0.538  & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 256 & --                  & --     & 1.60~$\times10^{3}$ & 0.592  & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 512 & --                  & --     & 1.83~$\times10^{3}$ & 0.581  & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000  \\
                    \hline
                    \hline
                    \multirow{9}{*}{\rotatebox[origin=c]{90}{\textbf{Glove-25}}}
                    & 1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 128 & --                  & --    & --                  & --    & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 256 & --                  & --    & --                  & --    & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000* \\
                    \hline
                    \hline
                    \multirow{8}{*}{\rotatebox[origin=c]{90}{\textbf{Sift}}}
                    & 1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\
                    \hline
                    \hline
                    \multirow{6}{*}{\rotatebox[origin=c]{90}{\textbf{Random}}}
                    & 1  & 1.17~$\times10^{4}$ & 0.060 & 4.28~$\times10^{3}$ & 0.028 & 7.34~$\times10^{2}$ & 1.000* & 5.54~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 2  & 1.01~$\times10^{4}$ & 0.048 & 4.04~$\times10^{3}$ & 0.021 & 3.58~$\times10^{2}$ & 1.000* & 2.69~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 4  & 9.12~$\times10^{3}$ & 0.031 & 3.64~$\times10^{3}$ & 0.014 & 1.90~$\times10^{2}$ & 1.000* & 1.37~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 8  & 8.35~$\times10^{3}$ & 0.022 & 3.37~$\times10^{3}$ & 0.013 & 8.84~$\times10^{1}$ & 1.000* & 5.69~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 16 & 8.25~$\times10^{3}$ & 0.008 & 3.17~$\times10^{3}$ & 0.006 & 4.36~$\times10^{1}$ & 1.000* & 2.61~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 32 & --                  & --    & 3.01~$\times10^{3}$ & 0.007 & 1.72~$\times10^{1}$ & 1.000* & 1.35~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}
